Relationship between solar wind, $D_{st}$, and plasmasphere mass density on one-hour time scales

### 2015-07-23 paper.tex
Updated code, comparing densities

\section{Appendix}
\subsection{Bias}
In an attempt to reproduce Figure 11 from \cite{Takahashi2010}, an ambiguity in data-handling was found. It is unknown how they got from hourly $\rho_{eq}$ to daily medians, whether in one step or two steps, so attempts were made to reproduce all possibilities and compare in order to find a data-handling method with the least bias. These attempts are shown in Figure \ref{blockmedian}. This also shows the effect of only considering events with a minimum before noon. All show a similar spike in $\rho_{eq}$ at the time of $D_{st}$ minimum, though none quite reproduce the exact values seen in \cite{Takahashi2010}. Figure \ref{allstorms} shows where the median falls for all of the found storms during that period, as a sanity check for why the prior work would get median values nearing $30 amu/cm^3$.

>>>>

\section{Appendix}
\subsection{Bias}
While attempting to reproduce Figure 11 from \cite{Takahashi2010}, an ambiguity in data-handling was found. It is unknown how they got from hourly $\rho_{eq}$ to daily medians, whether in one step or two steps, and whether the hourly medians are an hour ahead of each hour grid point, or a median of points a half hour to either side, so attempts were made to reproduce all possibilities and compare in order to find a data-handling method with the least bias. These attempts are shown in Figure \ref{blockmedian}. This also shows the effect of only considering events with a minimum before noon. All show a similar spike in $\rho_{eq}$ at the time of $D_{st}$ minimum, though none quite reproduce the exact values seen in \cite{Takahashi2010}. Figure \ref{allstorms} shows where the median falls for all of the found storms during that period, as a sanity check for why the prior work would get median values nearing $30 amu/cm^3$. Both authors of this paper conducted independent trials to confirm that the data and analysis don't quite yield the results of Figure 11 in \cite{Takahashi2010} with the processes described in that paper, but the same general trend is still seen.
